%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Philip D. Bulsink, BSc., MSc.
\documentclass[margin,line]{resume}
\topmargin 0mm

%______________________________________________________________________________________________________________________
\begin{document}
\thispagestyle{plain}
\name{\Large Philip D. Bulsink, B.Sc., M.Sc.}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}
        
    h: bulsinkp@gmail.com \hspace{60mm} w: philip.bulsink@canada.ca
\vspace{-4.5mm}
    
    https://github.com/pbulsink
    \\\vspace{-4.5mm}


    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Summary}

    A proven problem solver with expertise in computational, inorganic, and analytical chemistry.\\ Comfortable with aggressive learning curves and development of novel ideas.\\ Exploring data analysis using Python and R.


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of Ottawa}\\\vspace{1mm}%
    \textsl{Master's Degree} \hfill \textbf{2015}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Thesis: ``\textit{Rhenium\textsuperscript{I} Terdentate Compounds: Theoretical and Experimental Investigations}''
        \item Seminar: ``\textit{Recent Advances in NO\textsubscript{x} Abatement from Diesel Engine Emissions}''
        \item Tasks: Synthesis \& characterization of ligands and catalysts with novel photochemical properties.
        In-depth mechanism studies with various computational packages.
        Developed software in Python to simplify \& accelerate work.
        \item Supervisors: Dr. Tom Woo and Dr. Darrin Richeson
    \end{list2}

    \textbf{University of Waterloo}\\\vspace{1mm}%
    \textsl{Bachelor of Science, Honour's Chemistry, Co-op, Music Minor} \hfill \textbf{2012}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Honour's Thesis: ``\textit{Solid Sample Analysis by Microplasma Optical Emission Spectroscopy}''
    \end{list2}

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{Characterization Laboratory, CanmetENERGY, Natural Resources Canada} \hfill Ottawa \\\vspace{1mm}%
    \textsl{Fuels Chemist} \hfill \textbf{2014 -- Present}\\
    Perform method development and routine analysis, including HPLC, GC-MS, and GCxGC for solid, liquid and gaseous samples.
    Manage statistical control charts and other documentation for ISO9001 certification.
    Oversee instrument repair and maintenance.
    Represent laboratory at internal and external client meetings.
    

    \textbf{University of Ottawa, University of Waterloo} \hfill Ontario \\\vspace{1mm}%
    \textsl{Laboratory Teaching Assistant} \hfill \textbf{September 2011 -- May 2014}\\
    Teaching assistant for undergraduate labs in general, organic, inorganic, analytical, and physical chemistry.
    Demonstrated techniques and explained theoretical basis for experiments.

    \textbf{CanmetENERGY, Natural Resources Canada}\hfill Ottawa \\\vspace{1mm}%
    \textsl{Research Assistant - DeNO\textsubscript{x} Group} \hfill \textbf{May 2010 -- August 2011 (12 months total)}\\
    Research of homogeneous catalysts for removal of NO and NO\textsubscript{2} from lean-burn diesel engine exhaust.
    Improved catalyst testing procedures.
    Scaled catalyst synthesis by 3 orders of magnitude.
    Custom-built instrumentation and software for investigations.
    Prepared manuscripts for publishing.

    \textsl{Analytical Chemist - Characterization Laboratory} \hfill \textbf{January -- April 2009}\\
    Performed analysis of solid and liquid fuel samples.
    Designed and implemented a software based quality control monitoring system to assist ISO 9001:2000 compliance.
    Repaired analytical instruments.

    \textbf{Kinectrics Inc.}\hfill Etobicoke\\\vspace{1mm}%
    \textsl{Analytical Chemist} \hfill \textbf{September -- December 2009}\\
    Adhered to stringent ISO 17025 and ISO 14000 specifications while performing various chemical analysis.
    Prepared and tracked round-robin test samples for distribution to other laboratories.

\newpage
	\textbf{Philip D. Bulsink, B.Sc.} \hspace{279pt} Page 2 \\
	\vspace{-4mm}
    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honours and\\Distinctions} 

	Dean's Scholarship, University of Ottawa \hfill \textbf{2015}\vspace{1mm}\\
    Dean's Honour Roll, University of Waterloo, University of Ottawa \hfill \textbf{2011 -- 2014}\vspace{1mm}\\%
    Graduate Student Poster Award, CSC Inorganic Division Poster Symposium, Quebec City \hfill \textbf{2013}\vspace{1mm}\\%
    Recognition of Collaboration Award, CanmetENERGY, Natural Resources Canada \hfill \textbf{2012}\vspace{1mm}\\%
    Aileen Proudfoot Award, CanmetENERGY, Natural Resources Canada \hfill \textbf{2011}\vspace{1mm}\\%
    Outstanding Co-op ranking, University of Waterloo \hfill \textbf{2009 -- 2012}\vspace{1mm}%


    %__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Selected Publications}
    Bulsink, P. ``Transforming the Chemistry of Rhenium I: Physical and Theoretical Investigations'', \textit{Univeresity of Ottawa Thesis}, \textbf{2015}.

	Stanciulescu, M., Bulsink, P., Caravaggio, G., Nossova, L., Burich, R. ``NH3-TPD-MS study of Ce effect on the surface of Mn- or Fe-exchanged zeolites for selective catalytic reduction of NOx by ammonia'', \textit{App. Surface Sci.}, 300, pp. 201-207, \textbf{2014}.

	\vspace{0mm}
	Bulsink, P., Korobkov, I., Woo, T., Richeson, D. ``Transforming the chemistry of Re\textsuperscript{I} to access the Elusive Pincer Geometry'', \textit{CSC Inorganic Division Poster Symposium}, \textbf{2013}.

	\vspace{0mm}
    Stanciulescu, M., Caravaggio, G., Dobri, A., Moir, J,. Burich, R., Charland, J.-P., Bulsink, P. ``Low-temperature selective catalytic reduction of NOx with NH3 over Mn-containing catalysts'', \textit{App. Catal. B: Env.}, 123-124, pp. 229-240, \textbf{2012}.

	\vspace{0mm}
    Caravaggio, G., Stanciulescu, M., Burich, R., Scheier, B., Bulsink, P. ``Novel Catalysts for NOx Reduction with Reductants Produced In-Situ'', \textit{DEER Conference}, \textbf{2010}.
\vspace{1mm}

    %__________________________________________________________________________________________________________________
    % Activities
    \section{\mysidestyle Activities}

    \textbf{Giving Refugees Hope in Uganda}, Ottawa, Ontario, Canada\\\vspace{1mm}%
    \textsl{Co-Founder, Vice Chair} \hfill \textbf{January 2013 -- Present}\\
    Co-founded charitable organization assisting refugees in Kampala, Uganda.
    Administer projects, developed website, maintain online \& social media presence.
    Received charitable status from Canadian Revenue Agency in 8 months.

    \textbf{ChemCalculator.com}\\\vspace{1mm}%
    \textsl{Designer \& Programmer} \hfill \textbf{January 2013 -- Present}\\
    Developed website containing various chemistry calculations not available or not user-friendly elsewhere online.
    Direct application of self-taught and online course-based knowledge and principles of programming.

    \textbf{University of Waterloo}, Waterloo, Ontario, Canada\\\vspace{1mm}%
    \textsl{Residence Don} \hfill \textbf{May -- August 2009}\\
    Responsible for the well-being of 29 first and second year students.
    Counselled peers through personal and academic concerns.
    Organized floor and residence outings.
    Acted as a liaison between students and the Residence Manager.

	\textbf{Continuing Education}\\
	Completed (with verified certificate) portions of the `Data Science' specialization on Coursera, offered in partnership with Johns Hopkins University.
	
\vspace{1mm}
    %__________________________________________________________________________________________________________________
    % Affiliations
    \section{\mysidestyle Affiliations} 

    Chemical Institute of Canada (CIC), member 2011 -– Present


%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

