%! suppress = SuspiciousSectionFormatting
%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Philip D. Bulsink, BSc., MSc.
\documentclass[margin,line]{resumecls}
\usepackage[hidelinks]{hyperref}
\topmargin 0mm

%______________________________________________________________________________________________________________________
\begin{document}
\thispagestyle{plain}
\name{\Large Philip D. Bulsink \small{ B.Sc., M.Sc.}}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    personal: bulsinkp@gmail.com \hfill work: philip.bulsink@canada.ca%
    \vspace{-4.5mm}

    GitHub: https://github.com/pbulsink \hfill web: https://bulsink.ca/%
    \\\vspace{-4.5mm}

    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Summary}

    Analytical Chemist with a passion for problem-solving and a proven ability to leverage computational tools (R, VBA, Python) to develop novel solutions.
    Thrives in fast-paced environments, excelling at independent learning and driving innovative research efforts.


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of Ottawa}\\\vspace{1mm}%
    \textsl{Master's Degree} \hfill \textbf{2015}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Thesis: ``\textit{Rhenium\textsuperscript{I} Terdentate Compounds: Theoretical and Experimental Investigations}''
        \item Seminar: ``\textit{Recent Advances in NO\textsubscript{x} Abatement from Diesel Engine Emissions}''
        \item Tasks: Synthesis \& characterization of ligands and catalysts with novel photochemical properties.
        In-depth mechanism studies with various computational packages.
        Developed software in Python to simplify \& accelerate research.
        \item Supervisors: Dr. Tom Woo and Dr. Darrin Richeson
    \end{list2}

    \textbf{University of Waterloo}\\\vspace{1mm}%
    \textsl{Bachelor of Science, Honour's Chemistry, Co-op, Music Minor} \hfill \textbf{2012}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Honour's Thesis: ``\textit{Solid Sample Analysis by Microplasma Optical Emission Spectroscopy}''
    \end{list2}

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{Characterization Laboratory, CanmetENERGY, Natural Resources Canada} \hfill Ottawa \\\vspace{1mm}%
    \textsl{Fuels Chemist} \hfill \textbf{2014 -- Present}\\\vspace{-5mm}%
    \begin{list2}
        \item Pioneered advanced analytical methods using FTIR, HPLC, GC-MS, and GCxGC to unlock new insights from solid, liquid, and gaseous samples.
        \item Championed data quality by overseeing all liquid and gaseous sample analysis, personally verifying reported data, and leading ISO17025 internal audits.
        %\item Spearheaded international round-robin studies of Bio-Liquefaction oils, fostering collaboration and advancing scientific understanding of analytical methods.
        \item Cultivated strong client relationships by providing expert analysis recommendations and cost-effective experimental design.
        \item Acted as a scientific liaison at internal, external client, and international and committee meetings, representing the laboratory's, departmental, and Canadian scientific expertise.
        \item Contributed to research funding proposals, strengthening experimental design and improving project outcomes.
        %\item Actively participating in Emergency Response and Building Emergency and Evacuation teams.
    \end{list2}
    \textbf{University of Ottawa, University of Waterloo} \hfill Ontario \\\vspace{1mm}%
    \textsl{Laboratory Teaching Assistant} \hfill \textbf{September 2011 -- May 2014}\\\vspace{-5mm}%
    \begin{list2}
        \item Supervised undergraduate labs in General, Organic, Inorganic, Analytical, and Physical Chemistry, demonstrating techniques, explaining theoretical concepts, and ensuring safe and accurate experiment execution.
    \end{list2}

    \textbf{CanmetENERGY, Natural Resources Canada}\hfill Ottawa \\\vspace{1mm}%
    \textsl{Research Assistant - DeNO\textsubscript{x} Group} \hfill \textbf{May 2010 -- August 2011 (12 months total)}\\\vspace{-5mm}%
    \begin{list2}
        \item Investigated novel homogeneous catalysts for the reduction of nitrogen oxides (NO\textsubscript{x}) in lean-burn diesel engine exhaust.
        \item Scaled catalyst synthesis processes by 3 orders of magnitude.
        \item Custom-built instrumentation and software to support studies.
    \end{list2}

    %\textbf{Kinectrics, Inc.}\hfill Etobicoke \\\vspace{1mm}%
    %\textsl{Analytical Chemist} \hfill \textbf{September -- December 2009}\\\vspace{-5mm}
%
    %\textbf{Characterization Lab, CanmetENERGY, Natural Resources Canada} \hfill Ottawa \\\vspace{1mm}%
    %\textsl{Analytical Chemist - Characterization Laboratory} \hfill \textbf{January -- April 2009}\\

\newpage
%	\textbf{Philip D. Bulsink, B.Sc., M.Sc.} \hfill Page 2 \\  % Removed for ATS Resume readers
%	\vspace{-4mm}
    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honours and\\Distinctions}

    Excellence in Science - Departmental Achievement Award,  Natural Resources Canada\hfill\textbf{2023}\vspace{1mm}\\%
    Positive Workplace Impact - Energy Efficiency \& Technology Sector Award, Natural Resources Canada\hfill\textbf{2022}\vspace{1mm}\\%
    Innovation \& Creativity - CanmetENERGY-Ottawa Award, Natural Resources Canada\hfill\textbf{2021}\vspace{1mm}\\%
    Dean's Scholarship, University of Ottawa\hfill\textbf{2015}\vspace{1mm}\\%
    Dean's Honour Roll, University of Waterloo, University of Ottawa\hfill\textbf{2011 -- 2014}\vspace{1mm}\\%
    Graduate Student Poster Award, CSC Inorganic Division Poster Symposium, Quebec City\hfill\textbf{2013}\vspace{1mm}\\%
    Recognition of Collaboration - Departmental Achievement Award, Natural Resources Canada\hfill\textbf{2012}\vspace{1mm}\\%
    Aileen Proudfoot Award, CanmetENERGY, Natural Resources Canada\hfill\textbf{2011}\vspace{1mm}\\%
    Outstanding Co-op ranking, University of Waterloo\hfill\textbf{2009 -- 2012}\vspace{1mm}%


    %__________________________________________________________________________________________________________________-
    % Publications
    \section{\mysidestyle Selected Publications \& Presentations}
    Bulsink, P., Sant-Anna, S., Giddings, T., ``Quantification of components without direct calibration by GC-MS/PolyArc\textsuperscript \textregistered-FID'' \textit{American Chemical Society Conference}, \textbf{2023}

    \vspace{0mm}
    Bulsink, P., ``Results of the IEA Bioenergy Round Robin on the Analysis of Heteroatoms in Biomass Liquefaction Oils'' \textit{CanmetENERGY-Ottawa Science Seminar}, \textbf{2020}

    \vspace{0mm}
    Bulsink, P., de Miguel Mercader, F,. Sandström, L., Van De Beld, B., Preto, F., Zacher, A., Oasmaa, A., Dahmen, N., Funke, A., Bronson, B. ``Results of the International Energy Agency Bioenergy Round Robin on the Analysis of Heteroatoms in Biomass Liquefaction Oils'', \textit{Energy \& Fuels}, 34, 9, pp.\ 11123--11133, \textbf{2020}. \href{https://doi.org/10.1021/acs.energyfuels.0c02090}{10.1021/acs.energyfuels.0c02090}

    \vspace{0mm}
    Bulsink, P., Al-Ghamdi, A., Joshi, P., Korobkov, I., Woo, T., Richeson, D. ``Capturing Re(I) in a neutral N,N,N pincer scaffold and resulting enhanced absorption of visible light'', \textit{Dalton Trans.}, 45, pp.\ 8885--8896, \textbf{2016}.\href{https://doi.org/10.1039/C6DT00661B}{10.1039/C6DT00661B}

     \vspace{0mm}
    Bulsink, P. ``Transforming the Chemistry of Rhenium I: Physical and Theoretical Investigations'', \textit{University of Ottawa Thesis}, \textbf{2015}. \href{http://dx.doi.org/10.20381/ruor-2762}{10.20381/ruor-2762}

 	\vspace{0mm}
    Stanciulescu, M., Bulsink, P., Caravaggio, G., Nossova, L., Burich, R. ``NH3-TPD-MS study of Ce effect on the surface of Mn- or Fe-exchanged zeolites for selective catalytic reduction of NOx by ammonia'', \textit{App. Surface Sci.}, 300, pp.\ 201--207, \textbf{2014}. \href{https://doi.org/10.1016/j.apsusc.2014.01.175}{10.1016/j.apsusc.2014.01.175}

    \vspace{0mm}
    Richeson, D., Woo, T., Bulsink, P., Joshi, P., Jurca, T., Korobkov, I. ``Expanding the coordination geometry and enhancing the photophysical features of Re (I) with redox non-innocent pincer ligands'', \textit{American Chemical Society Conference}, \textbf{2014}.

	\vspace{0mm}
    Bulsink, P., Korobkov, I., Woo, T., Richeson, D. ``Transforming the chemistry of Re\textsuperscript{I} to access the Elusive Pincer Geometry'', \textit{CSC Inorganic Division Poster Symposium}, \textbf{2013}.

	\vspace{0mm}
    Stanciulescu, M., Caravaggio, G., Dobri, A., Moir, J,. Burich, R., Charland, J.-P., Bulsink, P. ``Low-temperature selective catalytic reduction of NOx with NH3 over Mn-containing catalysts'', \textit{App. Catal. B: Env.}, 123--124, pp.\ 229--240, \textbf{2012}. \href{https://doi.org/10.1016/j.apcatb.2012.04.012}{10.1016/j.apcatb.2012.04.012}

	\vspace{0mm}
    Caravaggio, G., Stanciulescu, M., Burich, R., Scheier, B., Bulsink, P. ``Novel Catalysts for NOx Reduction with Reductants Produced In-Situ'', \textit{DEER Conference}, \textbf{2010}.
\vspace{1mm}

    \newpage
    %__________________________________________________________________________________________________________________
    % Activities
    \section{\mysidestyle Activities}

    \textbf{f1dataR Package}\\\vspace{1mm}%
    \textsl{Author \& Maintainer} \hfill \textbf{2022 -- Present}\\\vspace{-5mm}%
    \begin{list2}
        \item Developed and maintain an R package that simplifies accessing Formula 1 data, leveraging a Python library
        %\item Ensured seamless data access by maintaining the R--Python interface via the `reticulate' package
        \item Responded to user and custodian feedback by addressing CRAN (Comprehensive R Archive Network) demands and handling issues raised on GitHub.
    \end{list2}

    \textbf{BulsinkBot}\\\vspace{1mm}%
    \textsl{Designer \& Programmer} \hfill \textbf{2018 -- Present}\\\vspace{-5mm}%
    \begin{list2}
        \item Developed and deployed predictive models for NHL hockey game, season, and playoff outcomes, achieving top-5 ranking in accuracy against professional and amateur models (2019-present).
        \item Leveraged data analysis to generate daily NHL predictions shared via social media platforms (Twitter, Mastodon, and BlueSky).
        \item Provided expert NHL predictions for dailyfaceoff.com for two seasons (2021--2022 and 2022--2023).
    \end{list2}

    \textbf{Emergency Response Team - CanmetENERGY, Natural Resources Canada}\\\vspace{1mm}%
    \textsl{Team Member \& Incident Commander} \hfill \textbf{2015 -- Present}\\\vspace{-5mm}%
    \begin{list2}
        \item Comprehensively trained in emergency medical and chemical response procedures, including first aid, burn response, trauma/wound care, and HAZMAT operations.
        \item Acted as backup dispatch, incident commander, and maintained annual SCBA recertification.
    \end{list2}

%    \textbf{ChemCalculator.com}\\\vspace{1mm}%
%    \textsl{Designer \& Programmer} \hfill \textbf{2013 -- 2017}\\ \vspace{-5mm}%
%    Developed website containing various chemistry calculations not available or not user-friendly elsewhere online.

%    \textbf{Giving Refugees Hope in Uganda}, Ottawa, Ontario, Canada\\\vspace{1mm}%
%    \textsl{Co-Founder, Vice Chair} \hfill \textbf{2013 -- 2016}\\\vspace{-5mm}
%    \begin{list2}
%        \item Co-founded charitable organization assisting refugees in Kampala, Uganda.
%        \item Administer projects, developed website, maintain online \& social media presence.
%        \item Received charitable status from Canadian Revenue Agency in 8 months.
%    \end{list2}

%    \textbf{University of Waterloo}, Waterloo, Ontario, Canada\\\vspace{1mm}%
%    \textsl{Residence Don} \hfill \textbf{May -- August 2009}\\\vspace{-5mm}%
%    \begin{list2}
%        \item Responsible for the well-being of 29 first and second year students.
%        \item Counselled peers through personal and academic concerns.
%        \item Organized floor and residence outings.
%        \item Acted as a liaison between students and the Residence Manager.
%    \end{list2}

    %\textbf{Continuing Education}\\
    %Completed the `Data Science' specialization on Coursera, offered in partnership with Johns Hopkins University.

\vspace{1mm}
    %__________________________________________________________________________________________________________________
    % Affiliations
    \section{\mysidestyle Affiliations}

    American Chemical Society (ACS), member 2019 -- Present

    \vspace{0mm}
    ASTM International, individual member 2024 -- Present

\end{resume}
\end{document}

